Spatial Analysis: Design-Based vs Model-Based

### 2021-01-26 draft.Rnw
minor updates

\begin{itemize}
  \item Design-Based Overview
    \begin{itemize}
      \item A classic text overviewing design-based approaches \citep{Sarndal2003model}
      \item A classic text overviewing design-based approaches \citep{Lohr2009sampling}
    \end{itemize}
  \item Model-Based Overview
    \begin{itemize}
      \item A classic text overviewing model-based approaches to analyzing spatial data \citep{Cressie2015statistics}
      \item A classic text overviewing model-based approaches to analyzing spatial data \citep{Schabenberger2017statistical}
    \end{itemize}
  \item Model-based and Design-based Comparisons
      \begin{itemize}
        \item A comparison of design-based and model-based approaches \citep{Hansen1983evaluation}
        \item A comparison of design-based and model-based approaches \citep{Brus1997random}
        \item A comparison of design-based and model-based approaches for spatial data \citep{VerHoef2002sampling}
        \item A comparison of design-based and model-based approaches for spatial data \citep{Cooper2006sampling}
        \item A comparison of design-based and model-based approaches\citep{sterba2009alternative}
        \item A comparison of design-based and model-based approaches for spatial data \citep{Brus2020statistical}
        \item A Bayesian approach to design-based approaches for spatial data \citep{Chan2020bayesian}
      \end{itemize}
  \item Spatially Balanced Design and Analysis
      \begin{itemize}
        \item GRTS sampling \citep{StevensOlsen2004GRTS}
        \item Local neighborhood variance estimation \citep{StevensOlsen2003VarianceEstimation}
      \end{itemize}
  \item Block Kriging 
      \begin{itemize}
        \item Finite Population Block Kriging (with an overview of Block Kriging) \citep{VerHoef2008spatial}
      \end{itemize}
\end{itemize}

>>>>

\subsection*{Why This Paper?}

We believe the distinction between these approaches is often misunderstood and there are several ways we could enchance the literature surrounding this topic:

\begin{enumerate}
  \item There are no comparisons in the literature between spatial model-based approaches and *spatially balanced* design approaches. From what we have seen, these comparisons are between spatial model-based approaches and independent random sample designs. While important to study this behavior, this comparison is no longer fair nor modern. Spatially balanced sampling has exploded in popularity throughout the last decade, and the design-based vs model-based literature needs to reflect this trend.
  \item A ``fair'' comparison 
  \item Misspecification
  \item Finite AND infinite populations
  \item Centered around the pragmatic questions practitioners will be faced with
  \item Provide reliable software

\end{enumerate}

\subsection*{Initial Literature}

\begin{itemize}
  \item Design-Based Overview \citep{Sarndal2003model, Lohr2009sampling}
  \item Model-Based Overview \citep{Cressie2015statistics, Schabenberger2017statistical}
  \item Design-Based and Model-Based Comparisons \citep{Hansen1983evaluation, Brus1997random, VerHoef2002sampling, Cooper2006sampling, sterba2009alternative, Brus2020statistical, Chan2020bayesian}
  \item Spatially Balanced Design and Analysis \citep{StevensOlsen2003VarianceEstimation, StevensOlsen2004GRTS}
  \item Finite Population Block Kriging \citep{VerHoef2002sampling, VerHoef2008spatial, Higham2020adjusting}
\end{itemize}

\subsection*{Potential Journals}
